---
title: "Diet Ordination, Clustering, and Plotting"
#output: html_notebook
---

# Ordinating Diet Shape file.  

Ordination of ordinal importance rankings, then using cluster analysis to determine clusters in the data. Then use 4 different discrete category schemes, and compare the clusters in multivariate diet space to the categories using the adjusted Rank Index. 


Load Packages and Data
```{r}
pacman::p_load(tidyverse, phytools, geiger, mclust, polycor, NbClust, ggstar, patchwork, here)

here::i_am("Code/Ord_Clust_Plot.Rmd")

#Functions
scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = na.rm)) / sd(x, na.rm)
add1 <- function(x, na.rm = TRUE) (x + 1)
# Read Tree
phylo <- ape::read.nexus(here("Data", "Carnivora_MCC_2.tre"))

# Read fossil data and calculate body size estimate ^1/3
fos_dat_1 <- read_csv(here("Data", "fossil_carnivoran_data.csv")) %>% 
  mutate(log_cuberoot_mass = log(mass_kg^(1/3)))
# Read extant data
dat <- read.delim(here("Data", "Master_Data.txt")) %>% 
  mutate(mass_kg = exp(log_cuberoot_mass)^3,
         phylo = Species) %>% 
  # drop taxa with missing m2 data
  drop_na(m2_dne) %>% 
  #combine extant and fossil dat for tip dropping and standardizing
  bind_rows(fos_dat_1) %>% 
  # Standardize all data together
  mutate_at(vars(4:11), scale2) %>% 
  mutate_at(vars(12:24), add1) %>% 
  mutate_at(vars(12:24), as.ordered) 
row.names(dat)<-dat$Species
# Remove extra tips (but keep fossil tips!)
carn_treedata<-treedata(phylo, dat, warnings = FALSE)
phylo<-carn_treedata$phy
dat1 <- dat %>% drop_na(bird)
```

#### Polychoric PC  

Now we need to generate the polychoric correlation matrix. We will use the polychor function in the polycor package to compute pairwise correlations between dietary item codings
```{r}
pcdat <- dat1 %>% select(12:24) %>% mutate_all(., as.numeric)

poly_mat <- matrix(data=NA, nrow=13, ncol=13)
rownames(poly_mat) <- colnames(poly_mat) <- colnames(pcdat)
for(i in 1:13) {
  for(j in 1:13) {
    if(i==j){
      tmp =1
    } else{
      tmp = polychor(x=pcdat[,i], y= pcdat[,j], ML=TRUE)
    }
     poly_mat[i,j] <- tmp
  } 
}
```
and then we can rotate the diet importance data by performing an eigendecomposition on the matrix 
```{r pca}
es = eigen(poly_mat);
means <-apply(pcdat, 2, mean)
ones <- as.matrix(rep(1, nrow(pcdat)))
S<- (as.matrix(pcdat)-(ones%*%means)) %*%es$vectors

#S is our matrix of PC scores. We can look at the percent variance explained by each pc by looking at the relative eigen values, the significant pcs by finding those with eigenvalues > 1, and the loadings by getting the correlations of the original variables with the pc axes.

# % variance explained
round(es$values/sum(es$values) *100, 2)
# significant pcs
which(es$values>1) 
# loadings
Loadings<-(t(pcdat) %*% S) / (nrow(pcdat)-1)
Loadings[,1:5]
```
Now add these values to the dat1 data frame 

```{r}
S2 <- as.data.frame(S) %>% 
  as_tibble(rownames = NA) %>% 
  rownames_to_column() %>% 
  rename(Species = rowname) %>% 
  left_join(dat1, by = 'Species')
```

## Mclust Clustering

Clustering Analyses with Mclust
The pineda scheme has 4 diet categories
THe van-Valkenburgh has 3 categories
Pantheria has 3 categories
ADW has 6

SO we need clustering analyses with 3, 4, and 6 clusters

```{r}
# This is the model selection process. G sets the number of possible clusters, default is 1:9
BIC <- mclustBIC(S2[,2:14], G = 1:20)
summary(BIC)
mod1 <- Mclust(S2[,2:14], x = BIC)
summary(mod1)
```

Model prefers 5, but not by much over 4 and 3. Call mod1  mod5

Best BIC values:
             VEI,5        VEI,4        VEI,3
BIC      -2856.415 -2857.808424 -2858.146864
BIC diff     0.000    -1.393356    -1.731795



Now make mod3, mod4, and mod6
```{r}
BIC3 <- mclustBIC(S2[,2:14], G = 3)
mod3 <- Mclust(S2[,2:14], x = BIC3)
cls3 <- as.data.frame(mod3$classification) %>% rename(class3 = "mod3$classification")

BIC4 <- mclustBIC(S2[,2:14], G = 4)
mod4 <- Mclust(S2[,2:14], x = BIC4)
cls4 <- as.data.frame(mod4$classification) %>% rename(class4 = "mod4$classification")

BIC5 <- mclustBIC(S2[,2:14], G = 5)
mod5 <- Mclust(S2[,2:14], x = BIC5)
cls5 <- as.data.frame(mod5$classification) %>% rename(class5 = "mod5$classification")

BIC6 <- mclustBIC(S2[,2:14], G = 6)
mod6 <- Mclust(S2[,2:14], x = BIC6)
cls6 <- as.data.frame(mod6$classification) %>% rename(class6 = "mod6$classification")
```
put it all together
```{r}
S3 <- S2 %>% bind_cols(cls3, cls4, cls5, cls6) %>% 
  mutate(class3 = as.factor(class3),
         class4 = as.factor(class4),
         class5 = as.factor(class5),
         class6 = as.factor(class6),
         Discrete = as.factor(Discrete))
```

```{r}
S3 %>% write_csv(here("Data", "mclust_diet_results.csv"))
```


# Matching Numbers of Clusters  
```{r}
S3 <- read_csv(here("Data", "mclust_diet_results.csv")) %>% mutate_at(c("class3", "class4", "class5", "class6"), as.factor)
```

### Van-Valk Results
```{r}
S3.1 <- S3 %>% drop_na(hopkins_van_valk)
Tvvk <- table(S3.1$hopkins_van_valk, S3.1$class3)
Tvvk
Rvvk <- adjustedRandIndex(S3.1$hopkins_van_valk, S3.1$class3)
Rvvk
```

### Pantheria Results
```{r}
S3.1 <- S3 %>% drop_na(pantheria)
Tpanth <- table(S3.1$pantheria, S3.1$class3)
Tpanth
Rpanth <- adjustedRandIndex(S3.1$pantheria, S3.1$class3)
Rpanth
```

### Piñeda Results
```{r}
S3.1 <- S3 %>% drop_na(hopkins_pineda)
Tpineda <- table(S3.1$hopkins_pineda, S3.1$class4)
Tpineda
Rpineda <- adjustedRandIndex(S3.1$hopkins_pineda, S3.1$class4)
Rpineda
```

### ADW Results
```{r}
S3.1 <- S3 %>% drop_na(Discrete)
Tadw <- table(S3.1$Discrete, S3.1$class6)
Tadw
Radw <- adjustedRandIndex(S3.1$Discrete, S3.1$class6)
Radw
```


### Plot

```{r}
ratpal <- c("1" = '#f48a1a', "3" = '#e6ab02', "2" = '#66a61e', "5" = 'tan4', "6" = '#0D7E9A', "4" ='#7570b3')
# Make Convex Hulls
hull <- S3 %>% 
  group_by(class6) %>% 
  slice(chull(V1, V2))
# Plot
S3  %>% ggplot(aes(x = V1, y = V2)) + 
  geom_star(aes(starshape = Discrete, fill = class6), size = 6, starstroke = 1) + 
  scale_starshape_manual(c(15, 13, 28, 23, 5, 14)) +
  geom_polygon(aes(color = class6, fill = class6), data = hull, alpha = 0.05) +
  scale_color_manual(values = ratpal) +
  scale_fill_manual(values = ratpal) +
  labs(x = "PC 1 (28%)", y = "PC 2 (18%)", title = "Animal Diversity Web\nAdj. Rand Index = 0.185") +
  guides(color = "none", fill = "none") +
  theme_classic() +
  theme(legend.title = element_blank(), 
        plot.title = element_text(size=18),
        legend.position = c(0.85, 0.95),
        panel.background = element_blank(),
        legend.background = element_rect(fill = "transparent"), # get rid of legend bg
        legend.key = element_rect(fill = "transparent", colour = NA), 
        legend.text=element_text(size=12),
        axis.text.y = element_text(angle = 90),
        panel.border = element_blank(),
        legend.key.size = unit(1.6, 'lines')) +
  coord_fixed() -> P1

ratpal <- c( "2" = '#e6ab02', "1" = '#66a61e',  "3" ='#7570b3')
hull <- S3 %>% drop_na(hopkins_van_valk) %>% 
  group_by(class3) %>% 
  slice(chull(V1, V2))
# Plot
S3  %>% drop_na(hopkins_van_valk) %>% ggplot(aes(x = V1, y = V2)) + 
  geom_star(aes(starshape = hopkins_van_valk, fill = class3), size = 6, starstroke = 1) + 
  scale_starshape_manual(c(15, 13, 28, 23, 5, 14)) +
  geom_polygon(aes(color = class3, fill = class3), data = hull, alpha = 0.05) +
  scale_color_manual(values = ratpal) +
  scale_fill_manual(values = ratpal) +
  labs(x = "PC 1 (28%)", y = "PC 2 (18%)", title = "Van Valkenburgh, 1988\nAdj. Rand Index = 0.145") +
  guides(color = "none", fill = "none") +
  theme_classic() +
  theme(legend.title = element_blank(),  
        plot.title = element_text(size=18),
        legend.position = c(0.81, 0.96),
        panel.background = element_blank(),
        legend.text=element_text(size=12),
        axis.text.y = element_text(angle = 90),
        panel.border = element_blank(),
        legend.key.size = unit(1.6, 'lines')) +
  coord_fixed() -> P2

hull <- S3 %>% drop_na(pantheria) %>%
  group_by(class3) %>% 
  slice(chull(V1, V2))
# Plot
S3  %>% drop_na(pantheria) %>% ggplot(aes(x = V1, y = V2)) + 
  geom_star(aes(starshape = pantheria, fill = class3), size = 6, starstroke = 1) + 
  scale_starshape_manual(c(15, 13, 28, 23, 5, 14)) +
  geom_polygon(aes(color = class3, fill = class3), data = hull, alpha = 0.05) +
  scale_color_manual(values = ratpal) +
  scale_fill_manual(values = ratpal) +
  labs(x = "PC 1 (28%)", y = "PC 2 (18%)", title = "PanTHERIA\nAdj. Rand Index = 0.021") +
  guides(color = "none", fill = "none") +
  theme_classic() +
  theme(legend.title = element_blank(),   
        plot.title = element_text(size=18),
        legend.position = c(0.81, 0.96),
        panel.background = element_blank(),
        legend.text=element_text(size=12),
        axis.text.y = element_text(angle = 90),
        panel.border = element_blank(),
        legend.key.size = unit(1.6, 'lines')) +
  coord_fixed()  -> P3


ratpal <- c( "3" = '#e6ab02', "2" = '#66a61e',  "4" ='#7570b3', "1" = '#f48a1a')
hull <- S3 %>% drop_na(hopkins_pineda) %>%
  group_by(class4) %>% 
  slice(chull(V1, V2))
# Plot
S3  %>% drop_na(hopkins_pineda) %>% ggplot(aes(x = V1, y = V2)) + 
  geom_star(aes(starshape = hopkins_pineda, fill = class4), size = 6, starstroke = 1) + 
     geom_polygon(aes(color = class4, fill = class4), data = hull, alpha = 0.05) +
  scale_starshape_manual(c(15, 13, 28, 23, 5, 14)) +
  scale_color_manual(values = ratpal) +
  scale_fill_manual(values = ratpal) +
  labs(x = "PC 1 (28%)", y = "PC 2 (18%)", title = "Piñeda-Munoz et al., 2017\nAdj. Rand Index = 0.158") +
  guides(color = "none", fill = "none") +
  theme_classic() +
  theme(legend.title = element_blank(),   
        plot.title = element_text(size=18),
        legend.position = c(0.78, 0.999),
        panel.background = element_blank(),
        legend.text=element_text(size=12),
        axis.text.y = element_text(angle = 90),
        legend.background = element_rect(fill = "transparent"), # get rid of legend bg
        legend.key = element_rect(fill = "transparent", colour = NA), 
        legend.key.size = unit(1.6, 'lines'),
        #legend spacing
        #legend.spacing.y = unit(2.0, 'cm'),
        panel.border = element_blank()) +
  coord_fixed()  -> P4

(P3 + P2) / (P4 + P1) + plot_annotation(tag_levels = 'A') &  theme(plot.tag = element_text(size = 18))
ggsave(here("Plots", "Figure_2_Diet_Clusters.png"), height = 11.9, width = 12.8)
ggsave(here("Plots", "Figure_2_Diet_Clusters.pdf"), height = 11.9, width = 12.8)
```

