---
title: "Prediction Figures"
---

# Prediction Figures 4 & 5

## Load Data and Packages  
```{r}
pacman::p_load(tidyverse, here, scico)

cryp_sp <- c("Arctogalidia_trivirgata", "Bassaricyon_alleni", "Catopuma_badia", "Chrotogale_owstoni", "Cynogale_bennettii", "Galidia_elegans", "Galidictis_fasciata", "Hemigalus_derbyanus", "Herpestes_brachyurus", "Mydaus_javanensis", "Paradoxurus_musanga", "Pardofelis_marmorata", "Prionodon_linsang")
#Load Fossil Taxa
fd <- read_csv(here("Data", "Crypt_Fos_Predictions_Summary.csv")) %>% 
  janitor::clean_names() %>% #select(species, item, wa_rank, ) %>% 
filter(!(species %in% cryp_sp)) %>% 
  mutate(species = str_replace_all(species, "_", " "),
         species = recode(species,
                          Dinictis = "Dinictis felina",
                          Miacis = "'Miacis' latidens"),
         item = str_replace_all(item, "_", " "),
         item = recode(item, 
                       bird = "Bird",
                       carrion = "Carrion",
                       egg = "Egg",
                       fish = "Fish",
                       fruit = "Fruit",
                       'hard invert' = "Hard Invert.",
                       herptile = "Herptile",
                       'large mammal' = "Large Mammal",
                       plant = "Plant",
                       root = "Root",
                       seed = "Seed",
                       'soft invert' = "Soft Invert.",
                       'small mammal' = "Small Mammal"
                       ))   

# Load Cryptic Taxa
cd  <- read_csv(here("Data", "Crypt_Fos_Predictions_Summary.csv")) %>% 
  janitor::clean_names() %>% 
filter(species %in% cryp_sp) %>% 
  mutate(species = str_replace_all(species, "_", " "),
         item = str_replace_all(item, "_", " "),
         item = recode(item, 
                       bird = "Bird",
                       carrion = "Carrion",
                       egg = "Egg",
                       fish = "Fish",
                       fruit = "Fruit",
                       'hard invert' = "Hard Invert.",
                       herptile = "Herptile",
                       'large mammal' = "Large Mammal",
                       plant = "Plant",
                       root = "Root",
                       seed = "Seed",
                       'soft invert' = "Soft Invert.",
                       'small mammal' = "Small Mammal"
                       )) 

```


## Heat-Map style  

Doing a heat-map style using geom_tile. I like this display personally

#### Fossil

Currently egg, root, and seed are deleted (all 1's, so they water down the figure)
THis makes a continuous grid with a discrete legend thanks to setting the width and height of the fill, turning off the color white (which makes the grids), adding the 'geude_legend' to the color paklette, and setting the legend.spacing.y. 


```{r}
fd %>% 
 ggplot(aes(x = item, y = species)) + 
  geom_tile(aes(fill = wa_rank, width = 0.92, height = 0.92),
            color = NA,
            lwd = 1,
            linetype = 1) +
  scico::scale_fill_scico(palette = "lajolla", begin  = 0.15, end = 1,
                          limits=c(1,4),
                          breaks = seq(1,4, by = 0.25),
                          labels = c( "1", "", "", "", "2", "", "", "", "3", "", "","", "4"),
                          guide = guide_legend(byrow = TRUE, reverse=T, size = 2)
                          ) +
  labs(fill='Dietary\nImportance\nRanking\n') +
  theme_minimal() +
  coord_fixed(ratio=1) +
  scale_y_discrete(limits=rev) +
  theme(axis.title.x=element_blank(),
        axis.text.x = element_text(angle = 45, 
                                   hjust = 1, 
                                   vjust = 1.1,  
                                   size=10),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y = element_text(face = "italic", 
                                   size=12),
        axis.ticks.y=element_blank(),
        panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        strip.background = element_blank(),
        panel.border = element_blank(),
        plot.background = element_blank(),
        legend.spacing.y = unit(-1, 'mm'),
        legend.key.height = unit(1, 'mm')) -> pred1

pred1
ggsave(here("Plots", "Fig_5_Fossil_Preds_Continuous.pdf"), width = 10, height = 8) 
ggsave(here("Plots", "Fig_5_Fossil_Preds_Continuous.png"), width = 7.5, height = 6)
```


#### Cryptic

```{r}
cd %>% 
 ggplot(aes(x = item, y = species)) + 
  geom_tile(aes(fill = wa_rank, width = 0.92, height = 0.92),
            color = NA,
            lwd = 1,
            linetype = 1) +
  scico::scale_fill_scico(palette = "lajolla", begin  = 0.15, end = 1,
                          limits=c(1,4),
                          breaks = seq(1,4, by = 0.25),
                          labels = c( "1", "", "", "", "2", "", "", "", "3", "", "","", "4"),
                          guide = guide_legend(byrow = TRUE, reverse=T, size = 2)
                          ) +
  labs(fill='Dietary\nImportance\nRanking\n') +
  theme_minimal() +
  coord_fixed(ratio=1) +
  scale_y_discrete(limits=rev) +
  theme(axis.title.x=element_blank(),
        axis.text.x = element_text(angle = 45, 
                                   hjust = 1, 
                                   vjust = 1.1,  
                                   size=10),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y = element_text(face = "italic", 
                                   size=12),
        axis.ticks.y=element_blank(),
        panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        strip.background = element_blank(),
        panel.border = element_blank(),
        plot.background = element_blank(),
        legend.spacing.y = unit(-1, 'mm'),
        legend.key.height = unit(1, 'mm')) -> pred2

pred2
ggsave(here("Plots", "Fig_4_Cryptic_Preds_Continuous.pdf"), width = 10, height = 8) 
ggsave(here("Plots", "Fig_4_Cryptic_Preds_Continuous.png"), width = 7.5, height = 6)
```
